Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
minor changes to section II

A recent paradigm in computational bioacoustics processes the audio stream in a holistic way over larger time scales, without assuming that a single species is present throughout the recording. Automated systems belonging to this paradigm attempt to infer global properties of bioacoustic scenes, including biodiversity indices \cite{Bardeli2010}, migration patterns \cite{Obrist2010}, as well as to detect time intervals of particular interest for detailed human inspection \cite{rosenstock2002landbird,diefenbach2007incorporating}.

@@

This statement has some support in auditory psychology as well as sound synthesis based on summary statistics \cite{mcdermott2013summary}. Indeed, studies in cognitive psychology investigating urban sound environment quality pointed out that global sound level (perceived or measured) is not sufficient to fully characterize an acoustic scene \cite{guyot2005urban,kang2006urban}. Rather, it seems that cognitive processes such as sound environment quality perception \cite{dubois2006cognitive} or loudness judgment \cite{kuwano_memory_2003} rely upon higher-level cognitive attributes such as the identities of the sound sources which compose the scene. It has been showed that, if available, the complete description of the scene in terms of event occurrences is powerful enough to reliably predict high-level cognitive classes, \eg the presence of birds are very likely to be heard in parks in urban areas and so are strong pleasantness indicators \cite{lafayPartI}. Consequently, research in sound perception is now strongly focused the contribution of specific sound sources in the assessment of a sound environment \cite{ricciardi2015sound,lavandier2006contribution}. Although the complete set of events occuring within a given auditory stream may not be discernable, even to human expects, research has shown that a small set of events, so-called markers, suffice to reliably predict many high-level attributes.

>>>>

A recent paradigm in computational bioacoustics processes the audio stream in a holistic way over larger time scales, without assuming that a single species is present throughout the recording. Automated systems belonging to this paradigm attempt to infer global properties of bioacoustic scenes, including biodiversity indices \cite{Bardeli2010}, migration patterns \cite{Obrist2010}, as well as to detect time intervals of particular interest befor detailed human inspection \cite{rosenstock2002landbird,diefenbach2007incorporating}.

@@

This statement has some support in auditory psychology as well as sound synthesis based on summary statistics \cite{mcdermott2013summary}. Indeed, studies in cognitive psychology investigating urban sound environment quality pointed out that global sound level (perceived or measured) is not sufficient to fully characterize an acoustic scene \cite{guyot2005urban,kang2006urban}. Rather, it seems that cognitive processes such as sound environment quality perception \cite{dubois2006cognitive} or loudness judgment \cite{kuwano_memory_2003} rely upon higher-level cognitive attributes such as the identities of the sound sources which compose the scene. It has been showed that, if available, the complete description of the scene in terms of event occurrences is powerful enough to reliably predict high-level cognitive classes, \eg the presence of birds are very likely to be heard in parks in urban areas and so are strong pleasantness indicators \cite{lafayPartI}. Consequently, research in sound perception is now strongly focused the contribution of specific sound sources in the assessment of a sound environment \cite{ricciardi2015sound,lavandier2006contribution}. Although the complete set of events occuring within a given auditory stream may not be discernable, even to human expects, research has shown that a small set of events, so called markers, suffice to reliably predict many high-level attributes.
